Paper 1

### 2022-06-15 scripts/Paper 1.Rmd
add days since jul1

@@

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-4]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[1] <- "jday"
colnames(rainfall_L)[3] <- "month"
rainfall_L$Site <- "L"
rainfall_L <- rainfall_L %>% filter(month >= 9)
rainfall_L$month <- as.numeric(rainfall_L$month) 
rainfall_L$month<- month.abb[rainfall_L$month]

@@

# define seasons
winter <- (rainfall$month == "6" | rainfall$month == "7" | rainfall$month == "8")
spring <- (rainfall$month == "9" | rainfall$month == "10" | rainfall$month == "11")
earlysummer <- (rainfall$month == "12")
latesummer <- (rainfall$month == "1" | rainfall$month == "2")
autumn <- (rainfall$month == "3" | rainfall$month == "4" | rainfall$month == "5")

@@

rainfall%>% ddply(c("Year", "season"), summarise,
                    seasonal.sum = sum(Precip, na.rm = TRUE))

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()
```

>>>>

input.daily$dayssinceJul1 <- ""

Grow19.20 <- input.daily[1:194,]
Grow19.20$dayssinceJul1 <- 1:194

Grow20.21 <- input.daily[195:559,]
Grow20.21$dayssinceJul1 <- 1:365

Grow21.22 <- input.daily[560:907,]
Grow21.22$dayssinceJul1 <-1:348

input.rearranged <- rbind(Grow19.20,Grow20.21, Grow21.22)
```

@@

#below is precip data from liaweenee - it only goes up to Jan 2022 right now
rainfall_L <- read.csv("R:/SET/PlantSci/Shared Work Spaces/Ecology/Peoples files/Marion Nyberg/PhD/Rainfall/rainfall.csv")
rainfall_L <- rainfall_L[-4]
colnames(rainfall_L)[4] <- "Precip"
rainfall_L$Year <- as.factor(rainfall_L$Year)
rainfall_L <- rainfall_L %>% filter(Year == 2019)
colnames(rainfall_L)[1] <- "jday"
colnames(rainfall_L)[3] <- "month"
rainfall_L$Site <- "L"
rainfall_L <- rainfall_L %>% filter(month >= 5)
rainfall_L$month <- as.numeric(rainfall_L$month) 
rainfall_L$month<- month.abb[rainfall_L$month]

@@

# define seasons
winter <- (rainfall$month == "Jun" | rainfall$month == "Jul" | rainfall$month == "Aug")
spring <- (rainfall$month == "Sep" | rainfall$month == "Oct" | rainfall$month == "Nov")
earlysummer <- (rainfall$month == "Dec")
latesummer <- (rainfall$month == "Jan" | rainfall$month == "Feb")
autumn <- (rainfall$month == "Mar" | rainfall$month == "Apr" | rainfall$month == "May")

@@

Seasonal.rain <- rainfall%>% filter(Year == 2020 | Year == 2021 | Year == 2022) %>% ddply(c("Year", "season"), summarise,
                    seasonal.sum = sum(Precip, na.rm = TRUE))

rain.aov <- aov(seasonal.sum~Year*season, data =Seasonal.rain)
summary(rain.aov)

TukeyHSD(rain.aov)
```
